\documentclass{article}
\usepackage{tabularx}
\topmargin -3.5cm
\usepackage[margin=0.5in]{geometry}
\usepackage{multirow}
\usepackage{Sweave}
\begin{document}
\input{alt_alt_syl-concordance}
\textbf{Alternate Community Ecology}\\
Community ecology is the study of organism and how they interact. It has a rich theoretical basis, a tradition of experimentation and observation and applied implications for the biolgical world around us. In this class we will integrate theory and evidence to see what it takes build and maintain communities from the ground up. \\
\scalebox{0.85}{
\begin{tabularx}{\columnwidth}{|p{4cm}|p{9cm}|p{5cm}|}
\hline
Subject & Topics & Reading \\
\hline
\multirow{3}{10em}{1] What is a community?} & Definitions  & Velland 1990 \\
& Measurements and Patterns of Diversity & Mittelbach Ch. 2  \\ 
& Species-Area relationships &   \\ 
\hline
\multirow{3}{10em}{2] Niche Theory} & Tradeoffs & Mich paper \\
& Character displacement &   \\ 
& Adaptive radiation &  Losos 2010 \\ 
\hline
\multirow{3}{10em}{3] Basic population models I } & Exponential  & Gotelli Ch. 1 \\
& Discrete &   \\ 
& Stochasticity &   \\ 
\hline
\multirow{3}{10em}{4] Basic population models II } & Logistic  & Gotelli Ch. 2 \\
& Carrying capacity &   \\ 
& Time lags &   \\ 
\hline
\multirow{3}{10em}{5] Life History } & Life history theory  & Stearns \\
& Fecundity schedules & Gotelli p.50-62  \\ 
& Life history evolution & paper() \\ 
\hline
\multirow{3}{10em}{6] Population genetics } & Gene flow  & LandGen exerpt  \\
& Locale adaptation &   \\ 
& Fragmentation and Bottlenecking & paper() \\ 
\hline
\multirow{3}{10em}{7] Metapopulation } & Migration  & Gotelli Ch. 4 \\
& Metapopulation model & Dingle 2007 \\ 
& Model modifications  &  \\ 
\hline
\multirow{3}{10em}{8] Competition Models } & Lokta-Volterra  & Gotelli p.100-114 \\
& Tilman's R* &  Mittelbach p.132-136  \\ 
& Isolclines  &  \\ 
\hline
\multirow{3}{10em}{9] Predation Models } & Lokta-Volterra  & Gotelli p.126-140 \\
& Functional response variation & Mittelbach p. 85-91   \\ 
& Isolclines  &  \\ 
\hline
\multirow{3}{10em}{10] Interactions in natural systems } & Competition  & Goldberg 1992 \\
& Predation & Sih 1985  \\ 
&  & Chase 2002 \\ 
\hline
\multirow{3}{10em}{11] Mutualisms } & Facilitation  & Mittelbach Ch. 9  \\
& Context dependency &   \\ 
& Case studies & Janzen 1966 \\ 
\hline
\multirow{3}{10em}{12]Eco-evo feedback } & Red queen  & Benton 2009 \\
& pollinator syndrome & Fenster 2004  \\ 
&  &  \\ 
\hline
\multirow{3}{10em}{13]Interaction networks I } & Type of Networks  & Mittelbach 198-205 \\
& Describing interactions &  Mittelbach 214-222 \\ 
& Measuring interaction strength &  \\ 
\hline
\multirow{3}{10em}{14]Interaction networks II } & Controls  & Mittelbach Ch. 11 \\
& Cascades & Beschta 2003  \\ 
& Case study & Beschta 2016 \\ 
\hline
\multirow{3}{10em}{15]Indirrect effects } & Interaction chain indirrect effects  & Morin Ch.8 \\
& interaction modification indirrect effects &   \\ 
&  & Amo 2014 \\ 
\hline
\multirow{3}{10em}{16] Disturbance } & Scale  & Connell 1978 \\
& Types & Wilkinson 1999  \\ 
& IDH & Fox 2013, Sheil 2013  \\ 
\hline
\multirow{3}{10em}{17] Succession } & Clements and Gleason  & Gleason 1939 \\
& Modeling & Gotelli 180-190  \\ 
& Case study &  del Moral 2014\\ 
\hline
\multirow{3}{10em}{18] Coexisitance } & Niche partitioning  & Silverton 2004 \\
& Storage effect &  Mittelbach p. 289-297  \\ 
& Fugative species & Mittlebach p. 260-263 \\ 
\hline
\multirow{3}{10em}{19] Community Assembly} & Metacommunities  & Leibold 2004 \\
& Historical Contigency &  Fukami 2015 \\ 
& Island Biogeography &  \\ 
\hline
\multirow{3}{10em}{20] Alternate Stable States} & Theory  & Mittelbach 304-313\\
& Novel Ecosystems &   \\ 
&  &  \\ 
\hline
\multirow{3}{10em}{21] Quaternary Biogeography} & refugia  &  \\
& migration &  Gavin 2014 \\ 
& Why are NA and China so similar? &  Tiffney 1985 \\ 
\hline
\multirow{3}{10em}{22] Community complexity and function} & Stability  & Tillman 1999 \\
& Function &  Mori 2018 \\ 
&  &  \\ 
\hline
\multirow{3}{10em}{23] Invasive species} & Framework & Sax 2007 \\
& Invasion &  Richardson 2006 \\ 
& Invaisability & Schlaepfer 2011  \\ 
\hline
\multirow{3}{10em}{24] Applications } & Restoration & \\
& Assisted Migration & Mclaughlan 2007  \\ 
& Rewilding & Donlan2005 \\ 
\hline
\end{tabularx}
}

\end{document}
